An Elastica-driven Digital Curve Evolution Model for Image Segmentation\thanks{This work has been partially funded by CoMeDiC ANR-15-CE40-0006 research grant.}

### 2019-12-20 answer-to-reviewers/answer-to-reviewers.tex

We thank the reviewers for their time, consideration and thoughtful comments. Our article has been amended
according to their recommendations. Changes in the text are highlighted in red. In addition, our replies follow.

\section{Reviewer \#1}

\paragraph{This is an interesting contribution to digital processing of images. Alternative approaches to discretization of elastica based on polygonal approximations for discrete elastica and their convergence issues could be mentioned for comparison}

~\\ In section 5, we indeed compare our segmentation model with the
work of \cite{schoenemann09linear}, which uses a polygonal
approximation of discrete elastica. In this work, the curvature is
estimated with a simple formula involving angle and edge lengths at
polygon vertices as proposed in \cite{bruckstein96}. This discrete
elastica problem with fixed end-points is proven to be
$\Gamma$-convergent toward the continuous elastica problem in
\cite{bruckstein01}. However it is not straightforward to include
image data term in this work, since the optimization variables of the
polygonal approximation are not related to the digital domain. For
instance, one could also use splines approximation with exact
curvature information and the same kind of approach would have the
same pros and cons.

### 2019-12-20 jmiv.tex
Intro parametric approaches

In fact, it is still a very challenging task to efficiently handle
curvature in the context of image segmentation.  State-of-art methods
are in practice difficult to optimize and do not scale easily
\cite{zehiry10fast,schoenemann09linear,strandmark11globalframework,nieuwenhuis14efficient}. In
order to achieve reasonable running times, such approaches make use of
coarse curvature estimations for which the approximation error is
often unknown. Improving the quality of the curvature estimator has an
important impact on the accuracy of the results, but is
computationally too costly in these methods. \revision{Moreover, parametric approaches to Elastica  as snakes and splines are too sensitive to the choice of anchor points and multigrid convergence hasn't been proven for them.}

>>>>

In fact, it is still a very challenging task to efficiently handle
curvature in the context of image segmentation.  State-of-art methods
are in practice difficult to optimize and do not scale easily
\cite{zehiry10fast,schoenemann09linear,strandmark11globalframework,nieuwenhuis14efficient}. In
order to achieve reasonable running times, such approaches make use of
coarse curvature estimations for which the approximation error is
often unknown. \revision{In the segmentation method of \cite{schoenemann09linear}, for example, the curvature is estimated by a simple formula involving angles and edge lengths at polygon vertices. The quality of the estimation is higly influenced by the number of vertices and where they are located along the curve. More important, in this estimator, the curve representation lies in the continuous domain and the properties of such estimator are not immediately valid when the curve is translated to the digital domain.  In particular, it is not straightforward to include a image data term in this model without adding extra assumptions about the curve representation. One could use a spline approximation with exact curvature information and the same kind of approach would have the same pros and cons.} Improving the quality of the curvature estimator has an important impact on the accuracy of the results, \revision{but we should use the appropriate tools to evaluate its quality. In the context of measurements in digital data, this tool is multigrid convergence.}

%Improving the quality of the curvature estimator has an
%important impact on the accuracy of the results, but is
%computationally too costly in these methods.

%\revision{Moreover, parametric approaches to Elastica  as snakes and splines are too sensitive to the choice of anchor points and multigrid convergence hasn't been proven for them.}
